Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-06-24 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

In order to evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}. However, these tools are based on simulation; they have the drawback of incomplete coverage since verification of all possible combinations, and potential failures of a system are not feasible~\cite{ClarkeHV18}. Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations. However, the industry demands the final solution to be the optimum, considering manufacturers, models, and brands available on the market and not just minimum or maximum powers and values for the optimized items, which can only be achieved with specialized PV optimization software.

Optimization of PV systems is not a recent topic; since the 1990s, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}. In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}. In $2017$, it was suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid ~\cite{Abate2017}. In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}. In $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}. However, \textit{formal methods and its application to synthesize PV systems are not explored in literature}.

>>>>

In order to evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}. However, these tools are based on simulation; \textcolor{blue}{they have the drawback of incomplete coverage} since verification of all possible combinations, and potential failures of a system are \textcolor{blue}{not feasible}~\cite{ClarkeHV18}. Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations. However, the industry demands the final solution to be the optimum, considering manufacturers, models, and brands available on the market and not just minimum or maximum powers and values for the optimized items, which can only be achieved with specialized PV optimization software.

Optimization of PV systems is not a recent topic; since the 1990s, different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical, and analytical methods, were proposed and developed~\cite{Alsadi2018}. In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}. \textcolor{blue}{In $2017$, it was suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid (e.g.,~\cite{Abate2017})}. In $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}. In $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}. However, \textit{formal methods and its application to synthesize PV systems are not explored in literature}.

### 2020-06-24 Tex/CAV2019/replyVSTTEJUNE2020.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{resposta}
Thank you, we corrected the the two occurrences to ``not feasible''.
\end{resposta}

@@

\begin{resposta}
Thank you, we corrected the text to ?In 2017, it was suggested the application...?.
\end{resposta}

>>>>

\begin{resposta}
We have replace ``infeasible'' by ``not feasible''.
\end{resposta}

@@

\begin{resposta}
We have rewritten this sentence as ``In $2017$, it was suggested the application of formal methods to verify and control the behaviour of computational devices in a smart grid [2]''.
\end{resposta}
